### 2022-06-05 manuscript.Rmd
Update manuscript.Rmd
Adjusting a citation

The EM algorithm needs starting values for each parameter it wants to estimate. 
If it were provided a single starting value for each parameter, 
the EM optimizer would be at risk of finding a local optimum instead of the global optimum. 
In other words, it would converge on a suboptimal solution resulting in biased parameter and model fit estimates. 
To prevent this, we should give the algorithm a sufficiently large set of random starting values for each parameter in order to maximize our chances of finding the deepest valley that is the global optimum (McLachlan & Peel, 2000). Furthermore, we should ensure the number of initial stage iterations is large for optimization to be successful (Geiser, 2012).

Furthermore, the choice of the starting values can impact the speed of the algorithm's convergence or in case of having poor initial values the algorithm might diverge altogether (McLachlan & Peel, 2000).
The key is to use a large number of starting value sets. Geiser (2013) recommends at least 500 sets of initial values in the first optimization step for simple models, and a greater number of sets for more complex models. A large number of starting values ensures that we find the true maximum and estimate the model parameters and fit accurately.

>>>>

The EM algorithm needs starting values for each parameter it wants to estimate. 
If it were provided a single starting value for each parameter, 
the EM optimizer would be at risk of finding a local optimum instead of the global optimum. 
In other words, it would converge on a suboptimal solution resulting in biased parameter and model fit estimates. 
To prevent this, we should give the algorithm a sufficiently large set of random starting values for each parameter in order to maximize our chances of finding the deepest valley that is the global optimum (McLachlan & Peel, 2004). Furthermore, we should ensure the number of initial stage iterations is large for optimization to be successful (Geiser, 2012).

Furthermore, the choice of the starting values can impact the speed of the algorithm's convergence or in case of having poor initial values the algorithm might diverge altogether (McLachlan & Peel, 2004).
The key is to use a large number of starting value sets. Geiser (2013) recommends at least 500 sets of initial values in the first optimization step for simple models, and a greater number of sets for more complex models. A large number of starting values ensures that we find the true maximum and estimate the model parameters and fit accurately.
